\documentclass[11pt]{letter}

\usepackage[hmargin={1.0in,1.0in},%
            vmargin={1.0in,1.0in},%
            nohead,%
            nofoot,%
            ]{geometry}                                 % the page layout without fancyhdr
\pagestyle{empty}

\begin{document}
\address{Ross Parker \\
Division of Applied Mathematics \\
Brown University \\
Providence, RI 02912 \\
\texttt{ross\_parker@brown.edu}}%
\signature{Ross Parker}
\begin{letter}{Editor, Physica D}

\opening{Dear Editor,}

On behalf of my co-authors, Panos Kevrekidis and Bj\"orn Sandstede, I would like to submit our revision of the article ``Existence and spectral stability of multi-pulses in discrete Hamiltonian lattice systems'' for consideration of publication in Physica D. 

We are grateful to the referees for their careful reading of the original manuscript, and their comments and suggestions regarding how we could improve it. The most significant change we have made is replacing the condition $R'(0) = J$ with the less restrictive ``commuting'' relation $R(\theta)J = J R^*(-\theta)$, which is (2.7) in Grillakis (1987). This makes the analysis more general, and it also connects the Melnikov sum $M$ to the stability criteria of Vakhitov-Kolokolov and Grillakis. Other than changing a few signs (e.g., for DNLS we now have $R(\theta) = -J$), the analysis is essentially unchanged. All the suggestions for improvement from the two reviewers have been systematically taken into
careful consideration, as noted below. Most of the revisied portions of the manuscript are indicated using red text.

Given the positive outlook of both reviewers and the
improvements made in accordance with the requests of the
Referees, we hope that you will now find the manuscript 
to be suitable for publication in Physica D. We will
be sincerely looking forward to your final editorial decision.

Reviewer 1
\begin{enumerate}
\item \emph{On page 2 the authors state that the relevant stability eigenvalues are close to zero. This is due to the rotation symmetry, as the problem being discrete (generically) rules out the translation symmetry. What happens if there is no underlying symmetry which leads to a zero eigenvalue for the primary pulse? Would it simply be the case that, assuming a certain transversality condition, if the primary pulse is orbitally stable, then any and all multi-pulses would be orbitally stable? I am thinking of the Grillakis-Shatah-Strauss (GSS) stability index theory here as the underlying theoretical justification for such a statement.}

\vspace{4mm}
This is briefly mentioned in the introduction and is discussed further in Section 3.5.
\vspace{4mm}

\item \emph{The model problem is the discrete NLS. Would the theory presented herein also apply to the discrete Klein-Gordon equation?}

\vspace{4mm}
The Referee is absolutely right as regards this Remark.
An analogous analysis of the steady state problem can be
carried out for fronts of the Klein-Gordon (KG) models, such as
the discrete sine-Gordon or the discrete $\phi^4$ models. 
While there are some differences between the two cases,
such as e.g. that for the KG models, we consider fronts rather
than pulses, and also that inter-site fronts are stable
(rather than on-site pulses for discrete NLS), nevertheless
the general Hamiltonian structure of the theory carries
through and multi-kink solutions and their stability
can be characterized in this framework. We note in passing that more complex, yet perhaps amenable
in some form to the present problem is the case of discrete
multi-breathers of Klein-Gordon models for which also 
extensive analysis has been done at the level of existence
and stability in recent years. 

In the revised manuscript, we briefly comment on the 
relevant possibilities and present associated references.
\vspace{4mm}

\item \emph{Just before Section 3 it is stated that the origin is an eigenvalue with geometric multiplicity (g.m.) one and algebraic multiplicity (a.m.) two. However, the argument leading up to that statement suggests that the g.m. is at least one, and the a.m. is at least two. I believe a further condition is needed to make the statement true.}

\vspace{4mm}
Without an additional assumption (i.e. transverse intersection in Hypothesis 4), the origin has geometric multiplicity at least one and algebraic multiplicity at least two. For clarity, the material about the kernel eigenvalues of DNLS has been moved to section 4 after the statement of Theorem 4. It is  mentioned there that with a transverse hypothesis assumption, the geometric multiplicity is exactly one.
\vspace{4mm}

\item \emph{I am confused as to why (20) and (21) essentially restate (12). Am I missing something?}

\vspace{4mm}
To avoid stating the same thing twice, this material has all been moved to section 3. 
\vspace{4mm}

\item \emph{Just before Section 3.2 we are told that $R'(0) = J$ is required. What happens if this condition fails? Or, can it not, because of the relationship between the symmetry and the associated conserved quantity?}

\vspace{4mm}
We have replaced the more restrictive condition $R'(0) = J$ by the commuting relation $R(\theta) J = J R^*(-\theta)$ from Grillakis (1987). In this generalized setting, the analysis is essentially unchanged. The main difference is the addition of Hypothesis 3, since the eigenvalues of $DF(0)$ can no longer be computed explicitly. We characterize the eigenvalues of $DF(0)$ following Hypothesis 3. Indeed, this is the most general setting for which, as far as
we can tell, the analysis through the techniques considered herein
can be carried through.
\vspace{4mm}

\item \emph{Equation (22) gives the underlying existence problem. How essential is it that the existence problem be written as a smooth first-order difference equation? In particular, would the results still go through if one simply assumed certain properties associated with the wave? Here I am thinking about problems where there is nonlinear coupling between sites, and it is not so easy to recast the problem as a first-order difference equation.}

\vspace{4mm}
Standard implementations of Lin's method, e.g. Knobloch (2000) for the discrete case, require that the problem be posed as a first order difference equation. For systems where this is difficult to do, e.g. the coupling between nodes is nonlinear, a different approach would be needed. We have added a comment to this effect in section 3.2.
\vspace{4mm}

\item \emph{Just above Section 4.2 it is stated that the spectral instability is due to Sturm-Liouville (SL) theory. As I understand [14], however, the instability follows from an application of the GSS theory, and SL is used simply to make some intermediate calculation. Am I wrong?}

\vspace{4mm}
It is correct that the instability follows from an application of the GSS theory, and SL is used for an intermediate calculation. 
Indeed, the Referee is correct here and we have accordingly
rephrased and rather than summarize the technique used in [14] (Ref. [18]
in the revised text), we have opted to include only the 
relevant reference (to avoid, in line with the suggestion
of the referee, confusing the reader).
\vspace{4mm}

\item \emph{In Theorem 5 it is assumed $M > 0$. What happens if $M < 0$?}

\vspace{4mm}
In Hypothesis 2 (of the revised manuscript), we assume $M > 0$, which is the Vakhitov-Kolokolov stability criterion (with the opposite sign) and stability criterion from Grillakis (1987). We do not consider the case $M < 0$ since that would imply instability of the principal pulse and hence that would, automatically, 
suggest that the waves that we construct would not stand a
chance to potentially be dynamically robust (i.e., spectrally stable).
We have added a brief relevant comment in the text.
\vspace{4mm}

\item \emph{On page 15 we are told about a pulse being ``highly discrete''. What does this mean? Does it have something to do with the decay rate? On a related note, if the decay rate is faster than exponential, does it effect the existence/spectral stability theory in any substantive way?}

\vspace{4mm}
The Referee is absolutely right that we did not define the
relevant notion of ``strong discreteness''.  In the AC limit, the pulse consists solely of a few sites (e.g. one or two) and multipulses
are a collection of multiple such entities. 
In the vicinity of such a limit, the pulses still only
``practically'' consist of a few sites (and a 
tail over small, exponentially decaying in space amplitudes).
Yet, to avoid including such a qualitative statement,
we have opted in the revised manuscript to remove 
the relevant phrase to avoid causing any confusion to the reader.
\vspace{4mm}

\item \emph{Reference [1] does not have an author.}

\vspace{4mm}
Fixed.
\vspace{4mm}

\end{enumerate}

Reviewer 2
\begin{enumerate}
\item \emph{Why not adding ``multi-pulse solutions'' and replacing ``discrete NLS equation'' with some- thing referring to ``Hamiltonian lattices'' (as in the title itself)? }

\vspace{4mm}
Done.
\vspace{4mm}

\item \emph{While the symmetry is exploited from the very beginning of the Mathematical Setup (see the standing wave ansatz for $\psi_n$), it is never mentioned in the Introduction (and in the Abstract too). There is an interplay between the symmetry and the hyperbolic structure, visible also in the difference between Hypothesis 3 and Hypothesis 5: by restricting to real-valued spatial profiles, one gets rid of the symmetry direction in the dNLS application (and the intersection between stable and unstable tangent manifolds reduces to the equilibrium).}

\vspace{4mm}
The symmetry is now mentioned in both the first sentence of the abstract and the introduction.
\vspace{4mm}

\item \emph{The possibility to extend existence and linear stability of multi-peaked discrete solitons beyond the anti-continuum and continuum limits should be stressed also in the Introduction, not only in the Conclusion: this point deserves some visibility.}

\vspace{4mm}
This is now mentioned in both the abstract and the introduction.
\vspace{4mm}

\item \emph{I think that some words should be added in the Introduction on the strategy used to construct multi-pulse solutions: for example, no words are spent to give a “taste” of Lin’s ideas (even heuristically, as made for example in the first pages of reference [19]) and on the need of taking the $m$ copies of the single pulse distant enough.}

\vspace{4mm}
A brief overview of Lin's method for the construction of a 2-pulse in the discrete case is given in the introduction. This is accompanied by an illustration.
\vspace{4mm}

\item \emph{The idea of decomposing multi-pulse solutions into overlapping single-pulse ones (restricted to the case of equally distinct pulse in the anti-continuum limit) reminds me a result of Pelinovsky and Sakovich in Nonlinearity 25(12) (see Lemma 1 formula (20) for a two-pulses). Also the scaling of the ``internal'' eigenvalues with respect to the parameters $d$, $N$ show similarities with this result (see Lemma, 2 Section 3).}

\vspace{4mm}
The similarity to the construction of multi-site breathers in Klein-Gordon lattices in Pelinovsky and Sakovich (2012) is noted in the material preceding Theorem 1. The similarity in the scaling of the eigenvalues is noted after Theorem 5. This is also mentioned in the introduction.
\vspace{4mm}

\item \emph{Hypothesis needed to get the result are not mentioned and commented, maybe because implicitly included in the reference to the Lin’s method. For all those who are not familiar with this mathematical method, this lack could prevent a proper understanding of the result. If not here, the Hypothesis should be commented at least in the Main Theorems part.}

\vspace{4mm}
We have added more explanatory text preceding each of the four hypotheses, which are the only hypotheses necessary for Lin's method to work for both the existence and the linear stability problem.
\vspace{4mm}

\item \emph{Formula (2): last $u_n$ should be a $\phi_n$.}

\vspace{4mm}
Fixed.
\vspace{4mm}

\item \emph{After formula (5), I would write ``The corresponding conserved quantity is given by''
instead of ``In addition...''.}

\vspace{4mm}
Done.
\vspace{4mm}

\item \emph{Before formula (9), isn’t the symmetric solution $R(\theta)u$ ``the same'' solution as $u$ (see also the statement before (18))?}

\vspace{4mm}
We clarified this point and noted how $\theta$ will be important for construction of multi-pulses.
\vspace{4mm}

\item \emph{It should be stated somewhere that $k$ is the ``lattice dimension'', so that $k = 1$ corresponds to the usual one-dimensional dNLS lattice. }

\vspace{4mm}
Done.
\vspace{4mm}

\item \emph{Is the map in Hypothesis 2 injective, so that there is a 1-to-1 correspondence between the frequency $\omega$ and the bound state $q$?}

\vspace{4mm}
We thank the Referee for this point and now discuss the injectivity in the relevant hypothesis as well as in a comment following the hypothesis that we do not distinguish between solutions $R(\theta)q$, which are just ``rotations'' of $q$.
\vspace{4mm}

\item \emph{After (25) the notation $Q(n)$ is used for an equilibrium of (22), while in the paragraph before (30) the same symbol stands for a homoclinic orbit. The context clarifies the different meanings, but maybe for the equilibrium a slightly different notation might be used.}

\vspace{4mm}
We clarified this by removing the notation $Q(n)$ after (25) so that $Q(n)$ now only refers to the homoclinic orbit.
\vspace{4mm}

\item \emph{Formula (39) looks like the so-called ``persistence condition'' which appear in other approaches: indeed, these are the equations providing the phase-shifts among the single pulses, as remarked before formula (134). This role of the ``vanishing-jumps condition'' should be stressed somewhere.}

\vspace{4mm}
We mention that this resembles persistence conditions from other approaches before Theorem 1. We thank the Referee for pointing out this similarity.
Indeed, we also now state the jump conditions for DNLS in terms of the phase differences $\Delta \theta_i$ before Theorem 4.
These conditions are rightfully reminiscent of the persistence
conditions from other approaches, such as, e.g., the ones
obtained in the vicinity of the anti-continuum limit.
Here, however, no such special assumptions have been
made and thus the conditions are formulated as a general
by-product of the application of Lin's method for the existence
of states involving multiple (well-separated) copies of a
single pulse.
\vspace{4mm}

\item \emph{In Remark 1, please make reference to the density current (10) already introduced.}

\vspace{4mm}
Done. Also introduced the term ``current density'' with equation (10).
\vspace{4mm}

\item \emph{Before Hypothesis 4 you speak about ``higher order Melnikov sum'': it suggests the idea that you are expanding a Melnikov function with respect to some parameter to get $M_2$. Unfortunately the reader is not helped to figure out to what expansion you are referring.}

\vspace{4mm}
$M > 0$ is now part of Hypothesis 2, and the connection is made to the stability criteria of Vakhitov-Kolokolov and Grillakis (1987). In the second remark following Hypothesis 2, we explain that the notation $M$ refers to the interpretation of $M$ as a Melnikov sum, since it measures a jump in a specific direction. The term ``higher order Melnikov sum'' is no longer used.

\vspace{4mm}

\item \emph{Is it possible to say something (in a dedicated Remark, for example) about how the ``threshold'' $N_0$ in Theorem 4 depends on $d$ and $\omega$?}

\vspace{4mm}
This is given in a remark after Theorem 4.
\vspace{4mm}

\item \emph{The definition of the Melnikov-like function $M$ should be numbered; moreover, since $M = \partial_\omega P$, with $P = \|q\|_{l^2}^2$, this assumption reminds me the Vakhitov-Kolokolov stability criterion, but no comments on this connection are given. Am I wrong?}

\vspace{4mm}
$M$ is now defined in Hypothesis 2 and is numbered. The connection to the stability criteria of Vakhitov-Kolokolov and Grillakis (1987) is made in the first remark after Hypothesis 2.
\vspace{4mm}

\item \emph{Corollary 1 deals exactly with the equally-spaced multi-pulses case, which I think might be compared with multi-site breathers in the above-mentioned paper by Pelinovsky and Sakovich.}

\vspace{4mm}
I mention this comparison after Corollary 1.
\vspace{4mm}

\item \emph{Consider additional papers by Pelinovsky and Sakovich; Bountis, et. al.; and Quin and Xiao.}

\vspace{4mm}
Peilnovsky and Sakovich (2012) has been referenced, as indicated above. The other two papers have been referenced, in the conclusion and after the statement of Theorem 4 (respectively).
\vspace{4mm}

\end{enumerate}

\closing{Cordially,}

\end{letter}
\end{document}
